Journal and article coverage

### 2025-02-17 analysis/manuscript.tex
Align with APA manual

\documentclass[a4paper,man,floatsintext,longtable,noextraspace,12pt]{apa6}

@@

@@

As a result of the comprehensive data processing described above,
datasets on open access in hybrid journals included in transformative
agreements were produced for each database at country and journal level
by year. Table~\ref{tbl-methods_overview_tab} provides a general
overview of the coverage between 2019 and 2023 per database. It shows
that the majority of hybrid journals published at least one original
article or review marked as core during the five-year period. These
journals formed the basis for the subsequent aggregation of publication
metrics.

>>>>

\documentclass[a4paper,man,floatsintext,longtable,noextraspace,10pt]{apa6}

@@

\setlength\parindent{1.27cm}

@@

As a result of the comprehensive data processing described above,
datasets on open access in hybrid journals included in transformative
agreements were produced for each database at country and journal level
by year. Table Table~\ref{tbl-methods_overview_tab} provides a general
overview of the coverage between 2019 and 2023 per database. It shows
that the majority of hybrid journals published at least one original
article or review marked as core during the five-year period. These
journals formed the basis for the subsequent aggregation of publication
metrics.
